\documentclass[12pt,conference]{IEEEtran}
\usepackage{standalone}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage{authblk}
\usepackage{textcomp}
\pagenumbering{arabic}

\title{Robotics in Healthcare}
\date{\today}
\author{Johnathan Aspinwall, Chris Card, Vicente Gonzalez, \\
Ryan Langewisch, Tim Nygren, Charles Tandy}

\begin{document}
\maketitle
\thispagestyle{plain}
\pagestyle{plain}
\input{Introduction}
\input{tnygren_heartlander}
\input{HeartLander_Part_2}
\input{RP-Vita_Part1}
\input{RP-Vita_Part2}
\input{ctandy_conclusion}
\appendix
Work Load:
\begin{itemize}
\item Johnathan Aspinwall: RP-Vita Part1: What makes it useful and how does it perceive its environment. 16\%
\item Chris Card: Team lead, Introduction, Document compilation. 20\%
\item Vicente Gonzales: HeartLander Part 2: What are its limitations and is it intelligent. 16\%
\item Ryan Langewisch: RP-Vita Part 2: What are its limitations and is it intelligent. 16\%
\item Tim Nygren: Heartlander Part 1: What makes it useful and how does it percive its environment. 16\%
\item Charles Tandy: Conclusion: What would the perfect robot and observations. 16\%
\end{itemize}

\begin{thebibliography}{4}
\bibitem{mellon}  Cameron Riviere. {\em HeartLander}. The Robotics Institute, Carnegie Mellon University. Sept. 7, 2014. http://www.ri.cmu.edu/research\_project\_detail.html?project\_id=
\newline 533\&menu\_id=261.
\bibitem{design}  Cameron Riviere. {\em HeartLander Design}. The Robotics Institute, Carnegie Mellon University. Sept. 7, 2014. http://www.cs.cmu.edu/\texttildelow{}./heartlander/design.html\#Locomotion.
\bibitem{overview}  Cameron Riviere. {\em HeartLander Overview}. The Robotics Institute, Carnegie Mellon University. Sept. 7, 2014. http://www.cs.cmu.edu/\texttildelow{}heartlander/.
\bibitem{results}  Cameron Riviere. {\em HeartLander Results}. The Robotics Institute, Carnegie Mellon University. Sept. 7, 2014. http://www.cs.cmu.edu/\texttildelow{}./heartlander/results.html.
\bibitem{irobot} Official website.  www.irobot.com/us/learn/commercial/rp-vita.aspx
\bibitem{spectrum} Evan Ackerman. {\em iRobot and InTouch Health Announce RP-VITA Telemedicine Robot}. http://spectrum.ieee.org/automaton/robotics/medical-robots/irobot-and-intouch-health-announce-rpvita-telemedicine-robot
% irobot - www.irobot.com/us/learn/commercial/rp-vita.aspx
% spectrum - http://spectrum.ieee.org/automaton/robotics/medical-robots/irobot-and-intouch-health-announce-rpvita-telemedicine-robot
\bibitem{Kerry} Kerry, Meghan. October 6, 2011. http://www.designnews.com/document.asp?doc\_id=233973\&dfp
\newline PParams=ht\_13,aid\_233973\&dfpLayout=article
\bibitem{Riviere} Riviere, Cameron.The Robotics Institute, Carnegie Mellon University. September 2011.  http://www.cs.cmu.edu/~./heartlander/index.html
\bibitem{Boston} Boston, MA. June 19, 2012. http://www.rethinkrobotics.com/news-item/heartland-robotics-inc-changes- name-to-rethink-robotics
\end{thebibliography}
\end{document}